Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-30 writeup/gz_hubble_data.tex
Subfigure package does not work with mnras

%\usepackage{epsfig}
\usepackage{color,soul}
%\usepackage{natbib}
\usepackage{deluxetable}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{url}
%\usepackage[normalem]{ulem}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\begin{figure*}
\centering

\subfigure{[a]\label{fig:smooth_to_smooth}\includegraphics[width=\textwidth]{figures/smooth_to_smooth.pdf}}

\subfigure{[b]\label{fig:smooth_to_int}\includegraphics[width=\textwidth]{figures/smooth_to_intermediate.pdf}}

\subfigure{[c]\label{fig:smooth_to_featured}\includegraphics[width=\textwidth]{figures/smooth_to_featured.pdf}}

\caption{Example images of GOODS galaxies that compare GZH morphological
classifications between their 2-epoch and 5-epoch imaging.  The top set (a)
were classified as ``smooth'' in both the 2- and 5-epoch imaging. The
middle set (b) was classified as ``smooth'' in the 2-epoch imaging and as
intermediate between ``smooth'' and ``featured'' in the 5-epoch imaging. The
bottom set (c) was classified as ``smooth'' in the 2-epoch imaging and
``featured'' in the 5-epoch imaging.}
\label{fig:shallow_smooth}
\end{figure*}

\begin{figure*}
\centering

\subfigure{[b]\label{fig:int_to_smooth}\includegraphics[width=\textwidth]{figures/intermediate_to_smooth.pdf}}

\subfigure{[b]\label{fig:int_to_int}\includegraphics[width=\textwidth]{figures/intermediate_to_intermediate.pdf}}

\subfigure{[b]\label{fig:int_to_featured}\includegraphics[width=\textwidth]{figures/intermediate_to_featured.pdf}}

\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
classified as ``intermediate'' in the 2-epoch imaging and ``smooth'' in the
5-epoch imaging. The middle set (b) was classified as intermediate in both the
2- and 5-epoch imaging. The bottom set (c) was classified as ``intermediate''
in the 2-epoch imaging and ``featured'' in the 5-epoch imaging.}
\label{fig:shallow_intermediate}
\end{figure*}

\begin{figure*}
\centering

\subfigure{[b]\label{fig:featured_to_smooth}\includegraphics[width=\textwidth]{figures/featured_to_smooth.pdf}}

\subfigure{[b]\label{fig:featured_to_int}\includegraphics[width=\textwidth]{figures/featured_to_intermediate.pdf}}

\subfigure{[b]\label{fig:featured_to_featured}\includegraphics[width=\textwidth]{figures/featured_to_featured.pdf}}

\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
classified as ``featured'' in the 2-epoch imaging and ``smooth'' in the 5-epoch
imaging (there were only six such images in the sample). The middle set (b) was
classified as ``featured'' in the 2-epoch imaging and ``intermediate'' in the
5-epoch imaging. The bottom set (c) was classified as ``featured'' in both the
2- and 5-epoch imaging.}
\label{fig:shallow_featured}
\end{figure*}

>>>>

%\usepackage{epsfig}
\usepackage{color,soul}
%\usepackage{natbib}
\usepackage{deluxetable}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
%\usepackage[normalem]{ulem}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/shallow_smooth.pdf}
\caption{Example images of GOODS galaxies that compare GZH morphological
classifications between their 2-epoch and 5-epoch imaging.  The top set
were classified as ``smooth'' in both the 2- and 5-epoch imaging. The
middle set was classified as ``smooth'' in the 2-epoch imaging and as
intermediate between ``smooth'' and ``featured'' in the 5-epoch imaging. The
bottom set was classified as ``smooth'' in the 2-epoch imaging and
``featured'' in the 5-epoch imaging (there are only seven such images
in the sample).}
\label{fig:shallow_smooth}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/shallow_intermediate.pdf}
\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
classified as ``intermediate'' in the 2-epoch imaging and ``smooth'' in the
5-epoch imaging. The middle set (b) was classified as intermediate in both the
2- and 5-epoch imaging. The bottom set (c) was classified as ``intermediate''
in the 2-epoch imaging and ``featured'' in the 5-epoch imaging.}
\label{fig:shallow_intermediate}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/shallow_featured.pdf}
\caption{Similar to Figure~\ref{fig:shallow_smooth}. The top set (a) were
classified as ``featured'' in the 2-epoch imaging and ``smooth'' in the 5-epoch
imaging (there were only six such images in the sample). The middle set (b) was
classified as ``featured'' in the 2-epoch imaging and ``intermediate'' in the
5-epoch imaging. The bottom set (c) was classified as ``featured'' in both the
2- and 5-epoch imaging.}
\label{fig:shallow_featured}
\end{figure*}
